Fusion Moves for Correlation Clustering

### 2014-11-10 paper/egpaper_for_review.tex
my changes

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
\usepackage{dirtytalk}
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
\usetikzlibrary{arrows,petri,topaths}
\usetikzlibrary{positioning,fit,calc}
\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
\usetikzlibrary{calc, matrix, backgrounds}

@@

\section{Energy Based Hierarchical Clustering (EHC)}

@@

@@

\subsection{Social Networks}
A application for large scale correlation clustering are social networks.
We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{http://snap.stanford.edu/data/index.html}.
Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 
%
The first network is called \emph{Epinions}. 
This is who-trust-whom online social network of a a general consumer review site Epinions.com. 
Each directed edge $a\to b$ indicated that user $a$ trusts  or does not trust user $b$ is the edge-weight is positive or negative, respectively.
The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
%
The first network is called \emph{Slashdot}. 
Slashdot is a technology-related news website know for its specific user community. 
In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friends or foes. 
The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges from which $76.73\%$ are positively weighted.

>>>>

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
\usepackage{dirtytalk}
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usepackage{scrextend}
\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
\usetikzlibrary{arrows,petri,topaths}
\usetikzlibrary{positioning,fit,calc}
\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
\usetikzlibrary{calc, matrix, backgrounds}

@@

\section{Energy Based Hierarchical Clustering (EHC)}\label{sec:ehc}

@@

Within all experiments we used the following existing solvers 
with public available implementation.
\begin{itemize}
    \item 
    \textbf{CGC} \cite{beier_2014_cvpr} we used the public available 
    implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}.
    As reported in \cite{beier_2014_cvpr}, CGC is faster and gives better energies then \cite{yarkony_2012_eccv} and \cite{bagon_2011_arxiv}.
    Therefore we exclude those in our experiments.
    \item \textbf{KL}\cite{???}  and a public available 
        implementation \footnote{
            \label{opengm-master} 
            \url{https://github.com/opengm/opengm}
            %\label{opengm-master}
        }
    \item \textbf{MC-R,MC-I}\cite{kappes_2011_emmcvpr}  where we used a  modified 
    version of a public available implementation implementation\footref{opengm-master}.
    We replace a highly used queue with a more suitable and
    fast \emph{index-min-heap}\cite{???}.
    MC-R indicates that only the LP is solved, while MC-I solves
    the ILP.
    \item non vision solvers here TODO
\end{itemize}
And the following proposed solvers:
\begin{itemize}
\item \textbf{EHC}: Energy Based Based Hierarchical Clustering 
as described in sec.~\ref{sec:ehc}.
\item \textbf{EHC-CGC}: As CGC but warm started 
with the solution from EHC.
\end{itemize}

@@

\subsection{Social Networks}
A application for large scale correlation clustering are social networks.
We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{\url{http://snap.stanford.edu/data/index.html}}.
Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 
%
The first network is called \emph{Epinions}. 
This is who-trust-whom online social network of a a general consumer review site Epinions.com. 
Each directed edge $a\to b$ indicated that user $a$ trusts  or does not trust user $b$ is the edge-weight is positive or negative, respectively.
The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
%
The first network is called \emph{Slashdot}. 
Slashdot is a technology-related news website know for its specific user community. 
In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friends or foes. 
The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges from which $76.73\%$ are positively weighted.
